Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-26 analysis/paper/paper.Rmd
Edit software section of results and tables

The most frequently cited software was `r names(which.max(table(rrpp$software_used)))`.
Other statistical software packages were frequently cited, SPSS (3rd) R (4th), GenStat and STATISTICA (7th).
The remainder were mostly specialised software except for Microsoft Excel in a 3-way tie for 9th (Table \@ref(tab:software-used)).

@@

```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
rrpp_software <-
  rrpp %>% 
  transform(software_used = strsplit(software_used, ",")) %>%
  unnest(software_used) %>%
  mutate(software_used = trimws(software_used)) %>%
  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise

rrpp_software %>%
  tabyl(software_used) %>%
  adorn_pct_formatting() %>%
  select(c(-percent, -valid_percent)) %>%
  rename(`Software Used` = software_used) %>%
  arrange(-n) %>%
  slice(seq_len(14)) %>%
  drop_na() %>%
  flextable() %>%
  autofit() %>%
  set_caption(
    "The top ten sofware programs that were found to be used in the papers that were surveyed."
  )
```

>>>>

```{r softwareCited, echo=FALSE, include=FALSE}
# tally up software used for the next paragraph
rrpp_software <-
  rrpp %>% 
  transform(software_used = strsplit(software_used, ",")) %>%
  unnest(software_used) %>%
  mutate(software_used = trimws(software_used)) %>%
  mutate(software_used = toupper(software_used))

tab <- table(rrpp_software$software_used)
tab_s <- as.data.frame(sort(tab))
tab_s <-
  tab_s %>%
  arrange(desc(Freq)) %>%
  filter(Freq %in% head(unique(Freq), 10)) %>% 
  rename("Software" = "Var1", "Frequency" = "Freq")
```

The most frequently cited software was `r tab_s[1, 1]`, where different versions were not distinguished.
The next three software packages were statistical software, `r tab_s[2, 1]`,  `r tab_s[3, 1]` and  `r tab_s[4, 1]` with two other statistical software packages frequently cited, GENSTAT and STATISTICA.
The remainder were mostly specialised software except for Microsoft Excel (Table \@ref(tab:software-used)).

@@

```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
tab_s %>%
  flextable() %>%
  autofit() %>%
  set_caption("The top ten sofware programs that were found to be used in the papers that were surveyed.")
```
